\documentclass[a4paper,12pt]{article}

% Process graphics.
\usepackage{graphicx}
% Create clickable links in the pdf
\usepackage[bookmarks=true,pdfborder={0 0 0}]{hyperref}

\usepackage{csquotes}
% Format links
\usepackage{url}

\usepackage[style=ieee]{biblatex}
\addbibresource{auxil/referencias.bib}

% Keep floats in their sections
\usepackage[section]{placeins}
% List code in the lstlisting environment
\usepackage{listings}
% Options for the lstlisting environment
\lstset{numbers=left, showspaces=false, showstringspaces=false, frame=single}
% Format tables with some special features (e.g. auto-width columns)
% \usepackage{tabulary}

%%%%% LEGACY LaTeX (pdflatex) - USE XeLaTeX IF AVAILABLE (SEE BELOW) %%%%%%%%%%
% Set the font to sans-serif
\renewcommand{\familydefault}{\sfdefault}
%%%%% ENABLE IF XeLaTeX or LuaLaTeX IS AVAILABLE FOR BEST RESULTS %%%%%%%%%%%%%
% Enables doing changes in the font.
% \usepackage{fontspec}
% Set the font. [Requires fontspec] If you don't have CMU Bright you can use another one, e.g. Arial.
% \setmainfont[Mapping=tex-text]{CMU Bright}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Enables setting cutom colors
\usepackage{xcolor}
\usepackage{sectsty}
\definecolor{blue1}{RGB}{52, 90, 138}
\definecolor{blue2}{RGB}{79, 129, 189}
\sectionfont{\color{blue1}}
\subsectionfont{\color{blue2}}
\subsubsectionfont{\color{blue2}}

\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{graphicx}

% --- Personalización de nombres para figuras y tablas en español ---
\renewcommand{\figurename}{Figura}
\renewcommand{\figureautorefname}{Figura}
\renewcommand{\tablename}{Tabla}
\renewcommand{\tableautorefname}{Tabla}

% Set the color of the Table of Contents header to black
\renewcommand{\contentsname}{\textcolor{black}{Table of Contents}}
% Set the title formatting
\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
    \begin{flushleft}
    {\Huge\textbf{\@title}}
    \end{flushleft}\egroup
}
\makeatother


% Typeset keystrokes
% \usepackage{keystroke}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\AtBeginEnvironment{tikzpicture}{\shorthandoff{:!<>|}}
\begin{document}

    % Set and insert the title.
    \title{Documento de diseño del sistema\\}
    \maketitle


    \section*{\color{black}Sentido del documento}

    Este documento describe el diseño del sistema de software para este proyecto.
    Se propondrán soluciones para los problemas de diseño y se describirán las decisiones de diseño tomadas.
    El documento de diseño del sistema (SDD) es un documento de referencia para el diseño del sistema de software y la arquitectura del software.
    Es un documento vinculante para el desarrollo del software y la implementación de los subsistemas.

    El contenido de este documento sigue y se ajusta a los requisitos especificados en el IEEE 1016--1998\autocite{IEEE1016-1998}


    % Set the Table of Contents depth and inert the ToC.
    \setcounter{tocdepth}{2}
    \tableofcontents


    \section{Introducción}\label{sec:introduccion}
    Este documento describe el diseño del sistema de software para el proyecto BiciFast.
    El diseño del sistema se basa en los requisitos funcionales y no funcionales especificados en el documento de requisitos del sistema (SRD).\autocite{SRD-BiciFast}
    Este documento está destinado a ser utilizado por los desarrolladores del sistema, los arquitectos de software y los diseñadores de la interfaz de usuario.

    \subsection{Propósito del documento}\label{subsec:proposito-del-documento}
    El propósito de este documento es proporcionar una descripción detallada del diseño del sistema de software para el proyecto BiciFast.

    \subsection{Definiciones, acrónimos y abreviaturas}\label{subsec:definiciones-acronimos-y-abreviaturas}


    \phantomsection

    \addcontentsline{toc}{section}{Referencias}


    \printbibliography


    \section{Objetivos de diseño}\label{sec:objetivos-de-diseno}
    Para diseñar este sistema, se ha priorizado:
    \begin{enumerate}
        \item \textbf{Modularidad:} Hacer que las partes del sistema sean independientes entre ellas, permitiendo la fácil modificación de los módulos.
        \item \textbf{Simplicidad:} Hacer que el sistema sea fácil de entender y de usar.
        \item \textbf{Separación de responsabilidades:} Separar las diferentes partes del sistema en módulos independientes, cada uno con su propia responsabilidad.
        \item \textbf{Escalabilidad:} Hacer que el sistema sea fácil de escalar y de modificar en el futuro.
    \end{enumerate}


    \section{Composición del sistema, arquitectura y capas}\label{sec:composicion-del-sistema-arquitectura-y-capas}
    \input{composición-del-sistema,-arquitectura-y-capas}

    \section{Diseño de la Interfaz Gráfica de Usuario (GUI)}\label{sec:diseno-de-la-interfaz-grafica-de-usuario-(gui)}
    \input{diseño-de-la-interfaz-gráfica-de-usuario-(gui)}
%
%    \section{Hardware/software mapping}
%    % Content: This section describes how the subsystems are mapped onto existing hardware and software components. A UML deployment diagram accompanies the description. The existing components are often off-the-shelf components. If the components are distributed on different nodes, the network infrastructure and the protocols are also described.
%    % NOTE: You may find a figure snippet at the end of this document.
%
%
%    \section{Persistent data management} % Optional
%    % Content: This section describes how the entity objects are mapped to persistent storage. It contains a rationale of the selected storage scheme, file system or database, a description of the selected database and database administration issues.
%
%
%    \section{Access control and security} % Optional
%    % Content: This section describes the access control and security issues based on the nonfunctional requirements in the requirements analysis document. It also describes the implementation of the access matrix based on capabilities or access control lists, the selection of authentication mechanisms and the use of encryption algorithms.
%
%
%    \section{Global software control} % Optional
%    % Content: This section describes the control flow of the system, in particular, whether a monolithic, event-driven control flow or concurrent processes have been selected, how requests are initiated and specific synchronization issues.
%
%
%    \section{Boundary conditions} % Optional
%    % Content: This section describes the use cases how to start up the separate components of the system, how to shut them down, and what to do if a component or the system fails.
%

\end{document}

